When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases\thanks{Part of this paper appeared at IJCAI \citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and \cref{section:models,section:labelled,section:filterverify} are new material.}

### 2017-10-15 paper/paper.tex
Plotting
Caption

    \caption{Behaviour of algorithms on the non-induced variant. For each plot, the x-axis is the
        pattern edge probability and the y-axis is the target edge probability, both from 0 to 1.
        Along the top row, we show the proportion of instances which are satisfiable; the white
        bands show the phase transitions, and the black lines are the predictions using
        equation~\eqref{equation:non-induced-prediction} of where the
        phase transition will occur. On the subsequent three rows, we show the number of search nodes used by the
        Glasgow, LAD and VF2 solvers; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

\clearpage
\appendix
\section{Reproducing These Experiments}

>>>>

    \caption{Behaviour of algorithms on the non-induced variant. For each plot, the x-axis is the
        pattern edge probability and the y-axis is the target edge probability, both from 0 to 1.
        Along the top row, we show the proportion of instances which are satisfiable; the white
        bands show the phase transitions, and the black lines are the predictions using
        equation~\eqref{equation:non-induced-prediction} of where the
        phase transition will occur. On the subsequent three rows, we show the number of search nodes used by the
        Glasgow, LAD and VF2 solvers; the dark regions indicate ``really hard'' instances, and black
        points indicate that at least one timeout occurred.}
    \label{figure:non-induced}
\end{figure}

@@
